### 2016-10-21 experiments.tex
new exp and MUSEUM stuff

The largest threat to validity is that this paper's conclusions rely on only two data sets, used in a previous paper.  The fault ground truths are possibly imperfect, due to the complex change history, and it was not possible to produce good patches for all faults, limiting our analysis of localization and explanation.  Generalizing to all compilers, or to software systems that are not compilers, would be unwarranted.  However, for compilers, we believe the underlying arguments supporting the probability of discovering many meaningful repairing mutants should hold in the general case.  There is no particular reason to believe that Csmith and {\tt jsfunfuzz} produce unusual random test cases, and both have often been used to detect faults in compilers other than the two considered in this paper.  For other kinds of software, more experiments are definitely warranted.  It is also possible that faults in the framework used for experiments introduced errors into the data.  In order to check for these problems, we will make the raw data for a re-analysis available on request.

>>>>

The largest threat to validity is that this paper's conclusions rely on only two data sets, used in a previous paper.  The fault ground truths are possibly imperfect, due to the complex change history, and it was not possible to produce good patches for all faults, limiting our analysis of fault localization.  Generalizing to all compilers, or to software systems that are not compilers, would be unwarranted.  However, for compilers, we believe the underlying arguments supporting the probability of discovering many meaningful repairing mutants should hold in the general case.  There is no particular reason to believe that Csmith and {\tt jsfunfuzz} produce unusual random test cases, and both have often been used to detect faults in compilers other than the two considered in this paper.  For other kinds of software, more experiments are definitely warranted.  It is also possible that faults in the framework used for experiments introduced errors into the data.  In order to check for these problems, we will make the raw data for a re-analysis available on request.
